Automated verification of stand-alone solar photovoltaic systems

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

PV systems are broadly classified into three distinct types~\cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system. %, where another source(s) of energy can work together with the solar PV. % system to provide the required demand.
%, such as wind, biomass or diesel, 
%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
%
%\begin{itemize}
%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants; 
%\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
%\end{itemize}
Specifically concerning the energy needed for remote rural areas of developing countries or places where the grid extension is not possible or feasible, 
%stand-alone systems are one the most used solutions, and 
% depending on the type of load, cost, resources availability, and requirements of the load, 
%stand-alone systems 
%can be split into several categories. However, 
the configuration that is most common or more suitable is the regulated stand-alone system with battery and AC load. This configuration is the focus of this study.
%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
%PV array, battery, MPPT and AC load. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}. Because of the AC load, an inverter (DC to AC converter) is required. 
%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.

@@

\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
%
In order to address different aspects of project system and systems design, there are various software tools \cite{Rajanna}, \cite{Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
 to complex financial analysis and project optimization. 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
Here it was evaluated the most popular ones, which are PVWatts, SAM, HOMER, RETScreen, and Hybrid2 \cite{NRELDobos}, \cite{NRELBlair}, \cite{Swarnkar}, \cite{Pradhan}, \cite{Mills}.

@@

Table~\ref{table:softwares} summarizes the off-the-shelf tools employed in this study, where only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis; 
additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis. RETScreen and HOMER have a free web-based version, but they have limited resources: it is not allowed to save the projects or even upload data from manufacturers. In other hand, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription range from US\$504.00 to US\$657.00.

@@

%-------------------------------------------------------------------
%\subsection{Paper Proposal x Reference Tools}
%-------------------------------------------------------------------
%
Considering the focus of this study, only HOMER remains for a comparative evaluation with our proposed automated verification technique. %All tools need some parameters inherently from manufacturer's catalog.
%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
The main challenge of this study is to show that it is possible to use automated verification in stand-alone PV solution, thus proving that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro. The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section~\ref{sec:results_indeed}.

@@

The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. In the diagram, there are two variables that depend on the site where the system is deployed and from the weather (solar irradiance $G$ and temperature $T$). For night hours or rainy days, one needs to hold batteries, where power can be stored and used. The use of battery as a storage form implies thus the presence of a charge controller~\cite{Hansen,Mellit}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
%
%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
%
\begin{figure}[h]
\includegraphics[width=0.48\textwidth]{blockdiagramPVS}
\centering
\caption{Block diagram for the stand-alone PV system (Source:~\cite{Hansen}).}
\label{fig:blockdiagram}
\end{figure}

@@

The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
is usually studied using an equivalent circuit model, as described in the available literature~\cite{Yatimi,Saloux,Mellit}. This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, in order to take into account energy losses in this model~\cite{Cubas}. 
%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
\begin{figure}[h]
\includegraphics[width=0.20\textwidth]{equivckt1D}
\centering
\caption{1-diode equivalent PV cell/panel circuit model (Source:~\cite{Cubas}).}
%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
\label{fig:equivckt}
\end{figure}

>>>>

PV systems are broadly classified into three distinct types~\cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system. %, where another source(s) of energy can work together with the solar PV. % system to provide the required demand.
%, such as wind, biomass or diesel, 
%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
%
%\begin{itemize}
%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants; 
%\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
%\end{itemize}
Specifically concerning the energy needed for remote rural areas of developing countries or places where the grid extension is not possible or feasible, 
%stand-alone systems are one the most used solutions, and 
% depending on the type of load, cost, resources availability, and requirements of the load, 
%stand-alone systems 
%can be split into several categories. However, 
the most suitable configuration is the regulated stand-alone system with battery and AC load. This configuration is the focus of this study.
%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
%PV array, battery, MPPT and AC load. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}. Because of the AC load, an inverter (DC to AC converter) is required. 
%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.

@@

\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
%
In order to address different aspects of project system and systems design, there are various software tools \cite{Rajanna}, \cite{Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
 to complex financial analysis and project optimization. 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
Here it was evaluated the most popular ones, which are PVWatts, SAM, HOMER, RETScreen, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.

@@

Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system or battery backup analysis. %all the tools perform solar photovoltaic analysis; 
Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis. RETScreen and HOMER have a free web-based version, but they have limited resources: it is not allowed to save the projects or even upload data from manufacturers. However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription range from US\$504.00 to US\$657.00.

@@

%-------------------------------------------------------------------
%\subsection{Paper Proposal x Reference Tools}
%-------------------------------------------------------------------
%
Considering the focus of this study, only HOMER remains for a comparative evaluation with our proposed automated verification technique. %All tools need some parameters inherently from manufacturer's catalog.
%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
The main challenge here is to demonstrate the use of automated verification in stand-alone PV solution, thus proving that this evaluation is more effective and complete than other state-of-the-art tool, as HOMER Pro. The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section~\ref{sec:results_indeed}.

@@

The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. In the diagram, there are two variables that depend on the site where the system is deployed and from the weather (solar irradiance $G$ and temperature $T$). For night hours or rainy days, one needs to hold batteries, where power can be stored and used. The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen,Mellit}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
%
%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
%
\begin{figure}[h]
\includegraphics[width=0.48\textwidth]{blockdiagramPVS}
\centering
\caption{Block diagram for the stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram}
\end{figure}

@@

The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
is usually studied using an equivalent circuit model~\cite{Yatimi,Saloux,Mellit}; this equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, in order to take into account energy losses in this model~\cite{Cubas}. 
%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
\begin{figure}[h]
\includegraphics[width=0.20\textwidth]{equivckt1D}
\centering
\caption{1-diode equivalent PV cell/panel circuit model (Source:~\cite{Cubas}).}
%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
\label{fig:equivckt}
\end{figure}
